---
title: "Hour 2"
---

# Installation and Basic Plot

## Objective:

Walk through the process of installing ggplot2 and any related packages, and demonstrate how to create a basic plot using ggplot2, including how to load data, specify the plot type, and customize the plot's appearance.

-   Installation: Explain how to install ggplot2 and any related packages.

    ```{r}
    # install ggplot2
    # install.packages("ggplot2")

    # install other related packages
    # install.packages("tidyverse")

    ```

-   Data: Explain how to load data in R and how to use ggplot2's functions to create visualizations with that data.

```{r}
# load data
data(mtcars)
```

```{r}
mtcars
```

-   Basic Plot: Demonstrate how to create a basic plot using ggplot2, including how to load data, specify the plot type, and customize the plot's appearance.

    ```{r}
    # import ggplot2 library
    library(ggplot2)

    # create a basic scatter plot
    ggplot(data = mtcars) +
      geom_point(mapping = aes(x = wt, y = mpg))

    ```

-   Customizing the Plot: Explain how to customize the plot's appearance using options such as color, shape, and size.

    ```{r}
    # import ggplot2 library
    library(ggplot2)

    # create a scatter plot with red color and different shape

    ggplot(data = mtcars) +
      geom_point(mapping = aes(x = wt, y = mpg), color = "red", shape = 1)

    ```

    ## Exercise:

-   Load any dataset of your choice and create a basic scatter plot using ggplot2.

-   Try customizing the plot by changing the color, shape, or size of the points.

-   Add a title and x-axis and y-axis labels to the plot.

This exercise will give you hands-on experience with creating a basic plot using ggplot2 and customizing it. It will also help you to understand how to load data and how to use the basic ggplot2 functions to create visualizations.
