---
title: "Hour 3"
---

# Aesthetics

## Objective:

Explain how to customize the plot's appearance using aesthetics such as color, size, shape, and more, and provide examples of how to use different aesthetics to create more engaging plots.

-   Aesthetics: Explain what aesthetics are and how they are used to customize the appearance of plots in ggplot2.

```{r}
# import ggplot2 library
library(ggplot2)

# create a basic scatter plot with color aesthetics
ggplot(data = mtcars) +
  geom_point(mapping = aes(x = wt, y = mpg, color = factor(cyl)))

```

-   Size and Shape: Explain how to use size and shape aesthetics to customize the appearance of points in a scatter plot.

```{r}
# create a scatter plot with size and shape aesthetics
ggplot(data = mtcars) +
  geom_point(mapping = aes(x = wt, y = mpg, size = hp, shape = factor(cyl)))

```

-   Grouping: Explain how to group points in a plot by a variable and how to use different aesthetics for different groups.

```{r}
# create a scatter plot grouped by a variable
ggplot(data = mtcars) +
  geom_point(mapping = aes(x = wt, y = mpg, color = factor(cyl), shape = factor(gear)))

```

-   Using Scale functions: Explain how to use scale functions to map aesthetics to specific values.

```{r}
# create a scatter plot using scale functions
ggplot(data = mtcars) +
  geom_point(mapping = aes(x = wt, y = mpg, size = hp, color = hp)) +
  scale_size_continuous(range = c(3, 8)) +
  scale_color_gradient(low = "blue", high = "red")

```

## Exercise:

-   Use any dataset of your choice and create a scatter plot with at least two aesthetics.

-   Try to group the points by a variable and use different aesthetics for different groups.

-   Use a scale function to map an aesthetic to specific values.

This exercise will give you hands-on experience with using aesthetics to customize the appearance of plots in ggplot2. It will also help you to understand how to group points by a variable and use different aesthetics for different groups and how to use scale functions to map aesthetics to specific values.
