---
title: "Hour 4"
author: "Mr. Denniz"
---

# Layers

## Objective:

### Show how to add layers to a plot, such as points, lines, and text, and how to customize their appearance.

-   Layers: Explain what layers are and how they are used to add different elements to a plot in ggplot2.

```{r}
# import ggplot2 library
library(ggplot2)

# create a basic scatter plot with a line
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg)) +
  geom_point() +
  geom_smooth(method = "lm")
      



```

-   Text: Explain how to add text to a plot and how to use different text elements such as labels, titles, and subtitles.

```{r}
# create a scatter plot with text labels
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg, label = rownames(mtcars))) +
  geom_point() +
  geom_text(size = 3, hjust = 0, nudge_x = 0.05)

```

Statistical Transformations: Explain how to use statistical transformations to add elements such as error bars, box plots, and violin plots to a plot.

```{r}
# create a scatter plot with error bars
ggplot(data = mtcars,mapping = aes(x = wt, y = mpg)) +
  geom_point() +
  geom_errorbar(mapping = aes(ymin = mpg - hp, ymax = mpg + hp))

```

-   Adding theme: Explain how to use ggplot2 theme elements to improve the appearance of the plot.

```{r}
# create a scatter plot with a theme
ggplot(data = mtcars) +
  geom_point(mapping = aes(x = wt, y = mpg)) +
  theme_classic()

```

## Exercise:

-   Use any dataset of your choice and create a scatter plot with at least one layer.

-   Add text to the plot, such as labels, titles, and subtitles.

-   Use a statistical transformation to add error bars, box plots, or violin plots to the plot.

-   Add a theme to the plot to improve its appearance.

This exercise will give you hands-on experience with adding layers to a plot in ggplot2 and customizing the appearance of those layers. It will also help you to understand how to use text and statistical transformations to add additional elements to a plot, and how to use themes to improve the overall appearance of the plot.

```{r}
mtcars

```
